State of the Practice for Lattice Boltzmann Method Software

### 2022-01-27 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
sorted table 5 LBM SOP paper

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3.5cm}p{2cm}p{2.5cm}p{2cm}p{2.5cm} }
			\toprule
			Name & Text Files & Binary Files & LOC & Avg.\ LOC / Text File\\
			\midrule
			DL\_MESO (LBE) & 310 & 51 & 170223 & 549\\
			ESPResSo & 1390& 83 & 195083 & 140\\
			ESPResSo++ & 1406& 30 & 165194 & 118\\
			HemeLB & 1102& 44 & 123806 & 112\\
			laboetie & 133& 1 & 48403 & 364\\		
			LatBo.jl & 41& 0 & 42172 & 1029\\
			LB2D-Prime & 82& 19 & 54755 & 668\\
			LB3D & 99 & 76 & 39766 & 402\\
			LB3D-Prime & 23& 6 & 12944 & 563\\
			lbmpy& 250 & 29 & 61632 & 247\\
			lettuce & 73 & 1 & 7660 & 105\\
			LIMBES & 26 & 1 & 4872 & 187\\
			Ludwig & 954 & 32 & 162518 & 170\\
			LUMA & 314 & 19 & 4399723 & 14011\\
			MechSys & 333 & 3 & 95707 & 287\\
			MP-LABS & 307 & 3 & 43124 & 140\\
			Musubi & 1347 & 1839 & 281879 & 209\\
			OpenLB & 1438 & 7 & 218406 & 152\\
			Palabos & 1974 & 71 & 563841 & 286\\
			pyLBM & 272 & 108 & 37234 & 137\\
			Sailfish & 632 & 11 & 69398 & 110\\
			SunlightLB & 36 & 1 & 7646 & 212\\
			TCLB & 594 & 7 & 49156 & 83\\
			waLBerla & 2643 & 69 & 873988 & 331\\
			\bottomrule
		\end{tabular}
		\caption{Module Data} \label{moduledata}
	\end{center}
\end{table}

>>>>

\begin{table}
	\begin{center}
		\begin{tabular}{ p{3.5cm}p{2cm}p{2.5cm}p{2cm}p{2.5cm} }
			\toprule
			Name & Text Files & Binary Files & LOC & Avg.\ LOC / Text File\\
			\midrule
			LUMA & 314 & 19 & 4399723 & 14011\\
			LatBo.jl & 41& 0 & 42172 & 1029\\
			LB2D-Prime & 82& 19 & 54755 & 668\\
			LB3D-Prime & 23& 6 & 12944 & 563\\
			DL\_MESO (LBE) & 310 & 51 & 170223 & 549\\
			LB3D & 99 & 76 & 39766 & 402\\
			laboetie & 133& 1 & 48403 & 364\\
			waLBerla & 2643 & 69 & 873988 & 331\\
			MechSys & 333 & 3 & 95707 & 287\\
			Palabos & 1974 & 71 & 563841 & 286\\
			lbmpy& 250 & 29 & 61632 & 247\\
			SunlightLB & 36 & 1 & 7646 & 212\\
			Musubi & 1347 & 1839 & 281879 & 209\\
			LIMBES & 26 & 1 & 4872 & 187\\
			Ludwig & 954 & 32 & 162518 & 170\\
			OpenLB & 1438 & 7 & 218406 & 152\\
			ESPResSo & 1390& 83 & 195083 & 140\\
			MP-LABS & 307 & 3 & 43124 & 140\\
			pyLBM & 272 & 108 & 37234 & 137\\
			ESPResSo++ & 1406& 30 & 165194 & 118\\
			HemeLB & 1102& 44 & 123806 & 112\\
			Sailfish & 632 & 11 & 69398 & 110\\
			lettuce & 73 & 1 & 7660 & 105\\
			TCLB & 594 & 7 & 49156 & 83\\
			\bottomrule
		\end{tabular}
		\caption{Module Data} \label{moduledata}
	\end{center}
\end{table}
